Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-12 submission5/core.tex
Use our property nicknames

Roessler and DeHon differentiate between memory safety policies (without lazy optimization)
and {\em data-flow integrity} policies (with lazy opimization.) Our properties
are phrased in terms of data flow, which corresponds to the optimized policies,
and which we argue is also sufficient to test non-optimized Depth Isolation.
Explicit formal properties are out of their scope, but they do list the
behaviors that they expect their data-flow integrity policies to prevent.
Data-flow integrity policies should prevent reads from sealed objects
(our caller confidentiality), should catch writes to sealed objects
if they are later read (our caller integrity), and should prevent reads
from deallocated objects (our callee confidentiality.)
They also note that Lazy Clearing prevents uninitialized reads,
which corresponds to our callee integrity.

>>>>

Roessler and DeHon differentiate between memory safety policies (without lazy optimization)
and {\em data-flow integrity} policies (with lazy opimization.) Our properties
are phrased in terms of data flow, which corresponds to the optimized policies,
and which we argue is also sufficient to test non-optimized Depth Isolation.
Explicit formal properties are out of their scope, but they do list the
behaviors that they expect their data-flow integrity policies to prevent.
Data-flow integrity policies should prevent reads from sealed objects
(\(\clrc\)), should catch writes to sealed objects
if they are later read (\(\clri\)), and should prevent reads
from deallocated objects (\(\clec\).)
They also note that Lazy Clearing prevents uninitialized reads,
which corresponds roughly to \(\clei\).
